---
title: "README"
author: "Chloe Chan"
output: github_document
---


#1: How many flights have a missing dep_time? What other variables are missing? What might these rows represent?

```{r}
a <-filter(nycflights13 :: flights, is.na(nycflights13::flights$dep_time))
nrow(a)


```

#1: There are 8255 flights that have a missing departure time. Other variables that are missing from this data are the arrival times, departure delay. These rows might represent the flights that were cancelled or rescheduled. 


#2: Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

```{r}
library(tidyverse)
flights <- nycflights13::flights
b <- transmute(flights,
    dep_time,
    dep_time_minutes = (dep_time %/% 100)*60 + (dep_time %% 100))
c <- transmute(flights,
    sched_dep_time,
    sched_dep_time_minutes = (sched_dep_time %/% 100)*60 + (sched_dep_time %% 100))
mutate(b, c)

```


#3: Look at the number of cancelled flights per day. Is there a pattern? Is the proportion of cancelled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with `ggplot(aes(x= ,y=)) + geom_point()'

```{r}
flights %>% group_by(year, month, day) %>% summarise(n_fcancel = sum(is.na(air_time) | air_time == 0),avg_arr_delay = mean(arr_delay, na.rm = TRUE), avg_dep_delay = mean(dep_delay, na.rm = TRUE) ) %>%
select(year, month, day, n_fcancel, avg_arr_delay, avg_dep_delay) %>%
filter(avg_arr_delay > 0) %>% ggplot()+ geom_point(aes(x = avg_arr_delay, y = n_fcancel, color = "red"))+ geom_point(aes(x = avg_dep_delay, y = n_fcancel,color =  "blue"))

```

The proportion of cancelled flights increases as the average delay time increases. 

Github Link: https://github.com/cchan88/443_homework_2



